Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-11-07 paper/paper.tex
No need to repeat the year

\title{Why Real-World Subgraph Matching is Easy, and \\ What This Means for Filter / Verify in
Graph Databases \thanks{Part of this paper appeared at IJCAI 2016
\citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and
\cref{section:models,section:labelled,section:filterverify} are new material.}}

>>>>

\title{Why Real-World Subgraph Matching is Easy, and \\ What This Means for Filter / Verify in
Graph Databases \thanks{Part of this paper appeared at IJCAI
\citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and
\cref{section:models,section:labelled,section:filterverify} are new material.}}
